---
title: "Analyse cell size"
output: html_notebook
---

Load libraries.
```{r}
library(Seurat)
library(future)
plan("multisession", workers = 1)
library(ggplot2)
library(interp)
library(rdist)
library(Matrix)
library(dplyr)
library(future)
library(BPCells)
options(future.globals.maxSize = 4000*1024^2)
source("seurat_utility_functions.R")
library(data.table)
library(lme4)
library(emmeans)
library(car)
library(lmerTest)
```

# Prepare cell and cluster metadata

Set dataset information.
```{r}
datasets_r1 = c("output-XETG00207__0034181__TA1__20240704__113512","output-XETG00207__0034181__TA2__20240704__113512","output-XETG00207__0034181__TA3__20240704__113512","output-XETG00207__0033712__TA4__20240704__113512","output-XETG00207__0033712__TA5__20240704__113512","output-XETG00207__0033712__TA6__20240704__113512")
names(datasets_r1) = c("TA1","TA2","TA3","TA4","TA5","TA6")
meta = c("V","P","L","V","P","L")
names(meta) =  c("TA1","TA2","TA3","TA4","TA5","TA6")

datasets_r2 = c("output-XETG00207__0033726__TA7__20240710__115843","output-XETG00207__0033726__TA8__20240710__115843","output-XETG00207__0033726__TA9__20240710__115843","output-XETG00207__0033724__TA10__20240710__115843","output-XETG00207__0033724__TA11__20240710__115843","output-XETG00207__0033724__TA12__20240710__115843")
names(datasets_r2) = c("TA7","TA8","TA9","TA10","TA11","TA12")
meta = c("V","P","L","V","P","L")
names(meta) =   c("TA7","TA8","TA9","TA10","TA11","TA12")
```

Read in cell meta data.
```{r}
cells = fread(paste0("../20240704__113302__040724_Tomo_mouse_gutroll_run1/", datasets_r1[["TA1"]],"/cells.csv.gz"))

cells$id = paste0("TA1-", cells$cell_id)
cells$sample = "TA1"

for (sample in  c("TA2","TA3","TA4","TA5","TA6")){
  cellsTemp = fread(paste0("../20240704__113302__040724_Tomo_mouse_gutroll_run1/", datasets_r1[[sample]],"/cells.csv.gz"))
  cellsTemp$id = paste0(sample,"-", cellsTemp$cell_id)
  cellsTemp$sample = sample
  cells = rbind(cells,cellsTemp)
}

for (sample in   c("TA7","TA8","TA9","TA10","TA11","TA12")){
  cellsTemp = fread(paste0("../20240710__115631__100724_Tomo_mouse_gutroll_run2/", datasets_r2[[sample]],"/cells.csv.gz"))
  cellsTemp$id = paste0(sample,"-", cellsTemp$cell_id)
  cellsTemp$sample = sample 
  cells = rbind(cells,cellsTemp)
}
```

Set directory.
```{r}
nuclei_directory = "../output/merged_analysis_nuclei/"
```

Read in meta data on clusters.
```{r}
nuclei_meta = read.csv(paste0(nuclei_directory,"nuclei_meta.csv"))
rownames(nuclei_meta) = nuclei_meta$cell_names
```

Filter cell meta data for those assigned clusters.
```{r}
cells_selected = cells[cells$id %in% nuclei_meta$cell_names,]
```

Set clusters information.
```{r}
cells_selected$cluster = nuclei_meta$epi_res0.5
```

Create directory for results.
```{r}
cell_stats_dir = paste0(nuclei_directory,"cell_stats/")
dir.create(cell_stats_dir)
```

Add meta data about condition and replicate.
```{r}
cells_selected$condition = ""
cells_selected$condition[cells_selected$sample %in% c("TA1","TA4","TA7","TA10")] = "Virgin"
cells_selected$condition[cells_selected$sample %in% c("TA2","TA5","TA8","TA11")] = "Pregnant"
cells_selected$condition[cells_selected$sample %in% c("TA3","TA6","TA9","TA12")] = "Lactating"

cells_selected$replicate = ""
cells_selected$replicate[cells_selected$sample %in% c("TA1","TA2","TA3")] = 1
cells_selected$replicate[cells_selected$sample %in% c("TA4","TA5","TA6")] = 2
cells_selected$replicate[cells_selected$sample %in% c("TA7","TA8","TA9")] = 3
cells_selected$replicate[cells_selected$sample %in% c("TA10","TA11","TA12")] = 4

cells_selected$condition = factor(cells_selected$condition, levels = c("Virgin","Pregnant","Lactating"))
cells_selected$replicate = factor(cells_selected$replicate)
```

Add information on log cell area.
```{r}
cells_selected$cell_area_log = log(cells_selected$cell_area)
cells_selected$nucleus_area_log = log(cells_selected$nucleus_area)
```


# Plot cell and nucleus area

Iterate through clusters and plot  cell and nucleus areas.
```{r}
for (i in seq(0,18,1)){
  print(i)
  
  selected = cells_selected[cells_selected$cluster == i,]
  
  p = ggplot(data = selected, aes(x = replicate, y = cell_area, color = condition)) + geom_violin() + geom_boxplot(width=0.1) + facet_wrap(~condition) + theme_classic() +
  theme(text = element_text(size = 20))
  print(p)
  ggsave(paste0(cell_stats_dir, "cell_area_cluster_", i, ".pdf"))
   p = ggplot(data = selected, aes(x = replicate, y = cell_area_log, color = condition)) + geom_violin() + geom_boxplot(width=0.1) + facet_wrap(~condition) + theme_classic() +
  theme(text = element_text(size = 20))
  print(p)
  ggsave(paste0(cell_stats_dir, "cell_area_log_cluster_", i, ".pdf"))
   p = ggplot(data = selected, aes(x = replicate, y = nucleus_area, color = condition)) + geom_violin() + geom_boxplot(width=0.1) + facet_wrap(~condition) + theme_classic() +
  theme(text = element_text(size = 20))
  print(p)
  ggsave(paste0(cell_stats_dir, "nucleus_area_cluster_", i, ".pdf"))
   p = ggplot(data = selected, aes(x = replicate, y = nucleus_area_log, color = condition)) + geom_violin() + geom_boxplot(width=0.1) + facet_wrap(~condition) + theme_classic() +
  theme(text = element_text(size = 20))
  print(p)
  ggsave(paste0(cell_stats_dir, "nucleus_area_log_cluster_", i, ".pdf"))
}
```


# Statistics for cell and nucleus area

Calculate statisics for cell area.
```{r}
all_emmeans = list()
all_contrasts = list()
all_coef = list()

for (i in seq(0,18,1)){
  print(i)
  selected = cells_selected[cells_selected$cluster == i,]
  print(dim(selected))
  
  # linear mixed-effects model 
  res = lmer(cell_area_log ~ condition + (1 | replicate/sample), data = selected)
  posthoc = emmeans(res, pairwise ~ condition)
  res = coef(summary(res))
  res = as.data.frame(res)
  res$cluster = i
  
  # post hoc
  means = as.data.frame(posthoc$emmeans)
  means$cluster = i
  contrasts =  as.data.frame(posthoc$contrasts)
  contrasts$cluster = i
  
  all_emmeans[[i+1]] = means
  all_contrasts[[i+1]] = contrasts
  all_coef[[i+1]] = res
}

write.csv(do.call(rbind, all_emmeans), paste0(cell_stats_dir, "emmeans_cell_size.csv"))

all_contrasts_df = do.call(rbind, all_contrasts)
all_contrasts_df$p.adj.overall = p.adjust(all_contrasts_df$p.value, method = "fdr")
write.csv(all_contrasts_df, paste0(cell_stats_dir, "contrasts_cell_size.csv"))

all_coef_df = do.call(rbind, all_coef)
write.csv(all_coef_df, paste0(cell_stats_dir, "lmer_cell_size.csv"))
```

Calculate statisics for nucleus area.
```{r}
all_emmeans = list()
all_contrasts = list()
all_coef = list()

for (i in seq(0,18,1)){
  print(i)
  selected = cells_selected[cells_selected$cluster == i,]
  print(dim(selected))
  
  # linear mixed-effects model 
  res = lmer(nucleus_area_log ~ condition + (1 | replicate/sample), data = selected)
  posthoc = emmeans(res, pairwise ~ condition)
  res = coef(summary(res))
  res = as.data.frame(res)
  res$cluster = i

  # post hoc
  means = as.data.frame(posthoc$emmeans)
  means$cluster = i
  contrasts =  as.data.frame(posthoc$contrasts)
  contrasts$cluster = i
  
  all_emmeans[[i+1]] = means
  all_contrasts[[i+1]] = contrasts
  all_coef[[i+1]] = res
}

write.csv(do.call(rbind, all_emmeans), paste0(cell_stats_dir, "emmeans_nucleus_size.csv"))

all_contrasts_df = do.call(rbind, all_contrasts)
all_contrasts_df$p.adj.overall = p.adjust(all_contrasts_df$p.value, method = "fdr")
write.csv(all_contrasts_df, paste0(cell_stats_dir, "contrasts_nucleus_size.csv"))

all_coef_df = do.call(rbind, all_coef)
write.csv(all_coef_df, paste0(cell_stats_dir, "lmer_nucleus_size.csv"))
```
