---
title: "Analyse cell type proportions"
output: html_notebook
---

Load libraries.
```{r}
library(Seurat)
library(future)
plan("multisession", workers = 8)
library(ggplot2)
library(interp)
library(rdist)
library(Matrix)
library(dplyr)
library(future)
library(BPCells)
options(future.globals.maxSize = 3000*1024^2)
source("seurat_utility_functions.R")
library(data.table)
library(speckle)
```

Set directory.
```{r}
nuclei_directory = "../output/merged_analysis_nuclei/"
```

Read in epithelial object.
```{r}
epi_nuc.obj = readRDS(paste0(nuclei_directory,"epi_merged_BPCells_projected.rds"))
```

# Run Propeller

Get transformed proportions.
```{r}
props = getTransformedProps(epi_nuc.obj$cluster_full[epi_nuc.obj$cluster_full != "19"], epi_nuc.obj$sample[epi_nuc.obj$cluster_full != "19"], transform="logit")
```

Check sample order.
```{r}
colnames(props$TransformedProps)
```

Set metadata.
```{r}
sample = colnames(props$TransformedProps)
condition = c("V","V","P","L","P","L","V","P","L","V","P","L")
slide = c("1","4","4","4","1","1","2","2","2","3","3","3")
```

Create design matrix.
```{r}
design = model.matrix(~ 0 + condition + slide)
design
```

Run Propeller anova test.
```{r}
anova.res = propeller.anova(prop.list=props, design=design, coef = c(1,2,3),
                robust=TRUE, trend=FALSE, sort=TRUE)
```

Write Propeller anova results to file.
```{r}
write.csv(anova.res,paste0(nuclei_directory,"propeller_results_res0.5_nuclei_clusters_updated.csv"))
```

# Post hoc tests 

Post hoc pairwise propeller T tests.
```{r}
mycontr = limma::makeContrasts(conditionV-conditionP, levels=design)
ttest_V_P = propeller.ttest(props, design, contrasts = mycontr, robust=TRUE, trend=FALSE, 
                sort=TRUE)

mycontr = limma::makeContrasts(conditionV-conditionL, levels=design)
ttest_V_L = propeller.ttest(props, design, contrasts = mycontr, robust=TRUE, trend=FALSE, 
                sort=TRUE)

mycontr = limma::makeContrasts(conditionP-conditionL, levels=design)
ttest_P_L = propeller.ttest(props, design, contrasts = mycontr, robust=TRUE, trend=FALSE, 
                sort=TRUE)
```

Adjust pvalues for multiple pairwise comparisons.
```{r}
pvals = c(ttest_V_P$P.Value,ttest_V_L$P.Value, ttest_P_L$P.Value)
p.adj.overall = p.adjust(pvals, method = "fdr")

ttest_V_P$FDR_overall = p.adj.overall[1:19]
ttest_V_L$FDR_overall = p.adj.overall[20:38]
ttest_P_L$FDR_overall = p.adj.overall[39:57]
```

Write results of Posthoc tests to file.
```{r}
write.csv(ttest_V_P,paste0(nuclei_directory,"propeller_results_V_P_res0.5_nuclei_clusters.csv"))
write.csv(ttest_V_L,paste0(nuclei_directory,"propeller_results_V_L_res0.5_nuclei_clusters.csv"))
write.csv(ttest_P_L,paste0(nuclei_directory,"propeller_results_P_L_res0.5_nuclei_clusters.csv"))
```

Version of analysis performing post hoc tests only on anova significant clusters.
```{r}
sig_clusters = rownames(anova.res)[anova.res$FDR < 0.05]
```

Filter proportions for significant clusters.
```{r}
props$Counts =  props$Counts[rownames(props$Counts) %in% sig_clusters,]
props$TransformedProps =  props$TransformedProps[rownames(props$TransformedProps) %in% sig_clusters,]
props$Proportions =  props$Proportions[rownames(props$Proportions) %in% sig_clusters,]
```

Post hoc pairwise propeller T tests.
```{r}
mycontr = limma::makeContrasts(conditionV-conditionP, levels=design)
ttest_V_P = propeller.ttest(props, design, contrasts = mycontr, robust=TRUE, trend=FALSE, 
                sort=TRUE)

mycontr = limma::makeContrasts(conditionV-conditionL, levels=design)
ttest_V_L = propeller.ttest(props, design, contrasts = mycontr, robust=TRUE, trend=FALSE, 
                sort=TRUE)

mycontr = limma::makeContrasts(conditionP-conditionL, levels=design)
ttest_P_L = propeller.ttest(props, design, contrasts = mycontr, robust=TRUE, trend=FALSE, 
                sort=TRUE)
```


Adjust pvalues for multiple pairwise comparisons
```{r}
pvals = c(ttest_V_P$P.Value,ttest_V_L$P.Value, ttest_P_L$P.Value)
p.adj.overall = p.adjust(pvals, method = "fdr")
ttest_V_P$FDR_overall = p.adj.overall[1:15]
ttest_V_L$FDR_overall = p.adj.overall[16:30]
ttest_P_L$FDR_overall = p.adj.overall[31:45]
```

Write results of Posthoc tests to file.
```{r}
write.csv(ttest_V_P,paste0(nuclei_directory,"propeller_results_V_P_res0.5_nuclei_clusters_only_anova_sig.csv"))
write.csv(ttest_V_L,paste0(nuclei_directory,"propeller_results_V_L_res0.5_nuclei_clusters_only_anova_sig.csv"))
write.csv(ttest_P_L,paste0(nuclei_directory,"propeller_results_P_L_res0.5_nuclei_clusters_only_anova_sig.csv"))
```

# Create plots

Format data.
```{r}
proportions = props$Proportions

proportions = melt(proportions, id.vars = "clusters")

proportions$condition = ""
proportions$condition[proportions$sample %in% c("TA1","TA4","TA7","TA10")] = "Virgin"
proportions$condition[proportions$sample %in% c("TA2","TA5","TA8","TA11")] = "Pregnant"
proportions$condition[proportions$sample %in% c("TA3","TA6","TA9","TA12")] = "Lactating"

proportions$replicate = ""
proportions$replicate[proportions$sample %in% c("TA1","TA2","TA3")] = 1
proportions$replicate[proportions$sample %in% c("TA4","TA5","TA6")] = 2
proportions$replicate[proportions$sample %in% c("TA7","TA8","TA9")] = 3
proportions$replicate[proportions$sample %in% c("TA10","TA11","TA12")] = 4

proportions$replicate = factor(proportions$replicate, levels = c(1,2,3,4))

proportions$clusters = factor(proportions$clusters, levels = 0:18)
proportions$condition = factor(proportions$condition, levels = c("Virgin", "Pregnant","Lactating"))
```

Set colour palette.
```{r}
pal = DiscretePalette(28, palette = "polychrome")
```

Create stacked bar plot.
```{r}
ggplot(proportions, aes(fill=clusters, y=value, x=replicate)) + 
    geom_bar(position="stack", stat="identity") + facet_wrap(~condition) + scale_fill_manual(values = pal) + theme_classic() +
  theme(text = element_text(size = 20))
ggsave(paste0(nuclei_directory, "cell_type_proportions_nuclei.pdf"))
```

