---
title: "Analyse Slc5a4a proportions"
output: html_notebook
---

Load libraries.
```{r}
library(Seurat)
library(future)
plan("multisession", workers = 8)
library(ggplot2)
library(Matrix)
library(dplyr)
library(future)
library(BPCells)
options(future.globals.maxSize = 3000*1024^2)
source("seurat_utility_functions.R")
library(data.table)
library(speckle)
```

Set directory.
```{r}
directory = "../output/merged_analysis_nuclei/"
```

# Format data for analysis

Read in epithelial object.
```{r}
epi.obj = readRDS(paste0(directory,"epi_merged_BPCells_projected.rds"))
```

Get counts for Slc5a4a.
```{r}
Slc5a4a = FetchData(epi.obj, vars = "Slc5a4a", layer = "counts") 
```

Check number positive cells.
```{r}
sum(Slc5a4a$Slc5a4a > 0)
```

Set categories based on Slc5a4a expression.
```{r}
epi.obj$Slc5a4a_status = "Slc5a4a_neg"
epi.obj$Slc5a4a_status[Slc5a4a$Slc5a4a > 0] = "Slc5a4a_pos"
```

Create directory for results.
```{r}
res_directory = paste0(directory, "Slc5a4a_proportions/")
dir.create(res_directory)
```

# Run Propeller

Get transformed proportions (omit cluster 19 as too few cells).
```{r}
props = getTransformedProps(epi.obj$Slc5a4a_status[epi.obj$cluster_full != "19"], epi.obj$sample[epi.obj$cluster_full != "19"], transform="logit")
```

Check sample order.
```{r}
colnames(props$TransformedProps)
```

Create meta data.
```{r}
sample = colnames(props$TransformedProps)
condition = c("V","V","P","L","P","L","V","P","L","V","P","L")
slide = c("1","4","4","4","1","1","2","2","2","3","3","3")
```

Create design matrix.
```{r}
design = model.matrix(~ 0 + condition + slide)
design
```

Run propeller anova.
```{r}
anova.res = propeller.anova(prop.list=props, design=design, coef = c(1,2,3),
                robust=TRUE, trend=FALSE, sort=TRUE)
```

Run post hoc propeller T tests.
```{r}
mycontr = limma::makeContrasts(conditionV-conditionP, levels=design)
ttest_V_P = propeller.ttest(props, design, contrasts = mycontr, robust=TRUE, trend=FALSE, 
                sort=TRUE)

mycontr = limma::makeContrasts(conditionV-conditionL, levels=design)
ttest_V_L = propeller.ttest(props, design, contrasts = mycontr, robust=TRUE, trend=FALSE, 
                sort=TRUE)

mycontr = limma::makeContrasts(conditionP-conditionL, levels=design)
ttest_P_L = propeller.ttest(props, design, contrasts = mycontr, robust=TRUE, trend=FALSE, 
                sort=TRUE)
```

Adjust p values for multiple testing
```{r}
pvals = c(ttest_V_P$P.Value,ttest_V_L$P.Value, ttest_P_L$P.Value)
p.adj.overall = p.adjust(pvals, method = "fdr")

ttest_V_P$FDR_overall = p.adj.overall[1:2]
ttest_V_L$FDR_overall = p.adj.overall[3:4]
ttest_P_L$FDR_overall = p.adj.overall[5:6]
```

Make directory for results.
```{r}
res_directory = paste0(directory, "Slc5a4a_proportions/")
dir.create(res_directory)
```

Write results to file
```{r}
write.csv(ttest_V_P,paste0(res_directory,"propeller_results_V_P_Slc5a4a.csv"))
write.csv(ttest_V_L,paste0(res_directory,"propeller_results_V_L_Slc5a4a.csv"))
write.csv(ttest_P_L,paste0(res_directory,"propeller_results_P_L_Slc5a4a.csv"))
write.csv(anova.res,paste0(res_directory,"propeller_results_Slc5a4a.csv"))
```

# Create plots

Format data.
```{r}
proportions = props$Proportions
proportions = melt(proportions, id.vars = "clusters")

proportions$condition = ""
proportions$condition[proportions$sample %in% c("TA1","TA4","TA7","TA10")] = "Virgin"
proportions$condition[proportions$sample %in% c("TA2","TA5","TA8","TA11")] = "Pregnant"
proportions$condition[proportions$sample %in% c("TA3","TA6","TA9","TA12")] = "Lactating"

proportions$replicate = ""
proportions$replicate[proportions$sample %in% c("TA1","TA2","TA3")] = 1
proportions$replicate[proportions$sample %in% c("TA4","TA5","TA6")] = 2
proportions$replicate[proportions$sample %in% c("TA7","TA8","TA9")] = 3
proportions$replicate[proportions$sample %in% c("TA10","TA11","TA12")] = 4

proportions$replicate = factor(proportions$replicate, levels = c(1,2,3,4))

proportions$clusters = factor(proportions$clusters, levels = c("Slc5a4a_neg","Slc5a4a_pos"))
proportions$condition = factor(proportions$condition, levels = c("Virgin", "Pregnant","Lactating"))
```

Create plot
```{r}
ggplot(proportions, aes(fill=clusters, y=value, x=replicate)) + 
    geom_bar(position="stack", stat="identity") + facet_wrap(~condition) + theme_classic() +
  theme(text = element_text(size = 20))
ggsave(paste0(res_directory, "Slc5a4a_proportions_nuclei.pdf"))#, height = 3, width = 6)
```

# Run propeller analysis for each cluster individually

Wrap above analysis in function.
```{r}
run_propeller_cluster = function(cluster){
  props = getTransformedProps(epi.obj$Slc5a4a_status[epi.obj$cluster_full == cluster], epi.obj$sample[epi.obj$cluster_full == cluster], transform="logit")
  print(cluster)
  print(colnames(props$TransformedProps))
  print(length(colnames(props$TransformedProps)))
  
  sample = colnames(props$TransformedProps)
  condition = c("V","V","P","L","P","L","V","P","L","V","P","L")
  slide = c("1","4","4","4","1","1","2","2","2","3","3","3")
  
  design <- model.matrix(~ 0 + condition + slide)
  design
  
  anova.res = propeller.anova(prop.list=props, design=design, coef = c(1,2,3),
                  robust=TRUE, trend=FALSE, sort=TRUE)
  
  mycontr = limma::makeContrasts(conditionV-conditionP, levels=design)
  ttest_V_P = propeller.ttest(props, design, contrasts = mycontr, robust=TRUE, trend=FALSE, 
                  sort=TRUE)
  
  mycontr = limma::makeContrasts(conditionV-conditionL, levels=design)
  ttest_V_L = propeller.ttest(props, design, contrasts = mycontr, robust=TRUE, trend=FALSE, 
                  sort=TRUE)
  
  mycontr = limma::makeContrasts(conditionP-conditionL, levels=design)
  ttest_P_L = propeller.ttest(props, design, contrasts = mycontr, robust=TRUE, trend=FALSE, 
                  sort=TRUE)
  
  pvals = c(ttest_V_P$P.Value,ttest_V_L$P.Value, ttest_P_L$P.Value)
  p.adj.overall = p.adjust(pvals, method = "fdr")
  
  ttest_V_P$FDR_overall = p.adj.overall[1:2]
  ttest_V_L$FDR_overall = p.adj.overall[3:4]
  ttest_P_L$FDR_overall = p.adj.overall[5:6]
  
  res_directory = paste0(directory, "Slc5a4a_proportions/")
  dir.create(res_directory)
  
  write.csv(ttest_V_P,paste0(res_directory,"propeller_results_V_P_Slc5a4a_cluster", cluster,".csv"))
  write.csv(ttest_V_L,paste0(res_directory,"propeller_results_V_L_Slc5a4a_cluster",cluster,".csv"))
  write.csv(ttest_P_L,paste0(res_directory,"propeller_results_P_L_Slc5a4a_cluster",cluster,".csv"))
  write.csv(anova.res,paste0(res_directory,"propeller_results_Slc5a4a_cluster",cluster,".csv"))
  proportions = props$Proportions
  proportions = melt(proportions, id.vars = "clusters")

  proportions$condition = ""
  proportions$condition[proportions$sample %in% c("TA1","TA4","TA7","TA10")] = "Virgin"
  proportions$condition[proportions$sample %in% c("TA2","TA5","TA8","TA11")] = "Pregnant"
  proportions$condition[proportions$sample %in% c("TA3","TA6","TA9","TA12")] = "Lactating"

  proportions$replicate = ""
  proportions$replicate[proportions$sample %in% c("TA1","TA2","TA3")] = 1
  proportions$replicate[proportions$sample %in% c("TA4","TA5","TA6")] = 2
  proportions$replicate[proportions$sample %in% c("TA7","TA8","TA9")] = 3
  proportions$replicate[proportions$sample %in% c("TA10","TA11","TA12")] = 4

  proportions$replicate = factor(proportions$replicate, levels = c(1,2,3,4))
  
  proportions$clusters = factor(proportions$clusters, levels = c("Slc5a4a_neg","Slc5a4a_pos"))
  proportions$condition = factor(proportions$condition, levels = c("Virgin", "Pregnant","Lactating"))

  ggplot(proportions, aes(fill=clusters, y=value, x=replicate)) + 
      geom_bar(position="stack", stat="identity") + facet_wrap(~condition) + theme_classic() +
    theme(text = element_text(size = 20))
  ggsave(paste0(res_directory, "Slc5a4a_proportions_nuclei_cluster",cluster,".pdf"))
}
```

Iterate through clusters and run propeller.
```{r}
for (cluster in unique(epi.obj$cluster_full)){
  try(run_propeller_cluster(cluster))
}
```

