---
title: "Main analysis of Xenium data for 'Growth of the maternal intestine during reproduction'"
output: html_notebook
---

Load packages.
```{r}
library(Seurat)
library(future)
plan("multisession", workers = 8)
library(ggplot2)
library(interp)
library(rdist)
library(Matrix)
library(dplyr)
library(future)
library(BPCells)
options(future.globals.maxSize = 12000*1024^2)
source("seurat_utility_functions.R")
library(data.table)
library(patchwork)
```

# Read in data

Set dataset info for run 1.
```{r}
datasets_r1 = c("output-XETG00207__0034181__TA1__20240704__113512","output-XETG00207__0034181__TA2__20240704__113512","output-XETG00207__0034181__TA3__20240704__113512","output-XETG00207__0033712__TA4__20240704__113512","output-XETG00207__0033712__TA5__20240704__113512","output-XETG00207__0033712__TA6__20240704__113512")
names(datasets_r1) = c("TA1","TA2","TA3","TA4","TA5","TA6")
meta = c("V","P","L","V","P","L")
names(meta) =  c("TA1","TA2","TA3","TA4","TA5","TA6")
```

Read in raw counts and meta data for run 1.
```{r}
mat = Read10X_h5(paste0("../20240704__113302__040724_Tomo_mouse_gutroll_run1/", datasets_r1[["TA1"]],"/nuclei_data.h5"))
colnames(mat) = paste0("TA1-",colnames(mat))
meta_data = data.frame(cell = colnames(mat), sample = "TA1", condition =  meta["TA1"])

for (sample in c("TA2","TA3","TA4","TA5","TA6")){
  print(sample)
  mat_tmp = Read10X_h5(paste0("../20240704__113302__040724_Tomo_mouse_gutroll_run1/", datasets_r1[[sample]],"/nuclei_data.h5"))
  colnames(mat_tmp) = paste0(sample,"-",colnames(mat_tmp))
  meta_data = rbind(meta_data,data.frame(cell = colnames(mat_tmp), sample = sample, condition =  meta[sample]))
  mat = cbind(mat, mat_tmp)
}
```

Set dataset info for run 2.
```{r}
datasets_r2 = c("output-XETG00207__0033726__TA7__20240710__115843","output-XETG00207__0033726__TA8__20240710__115843","output-XETG00207__0033726__TA9__20240710__115843","output-XETG00207__0033724__TA10__20240710__115843","output-XETG00207__0033724__TA11__20240710__115843","output-XETG00207__0033724__TA12__20240710__115843")
names(datasets_r2) = c("TA7","TA8","TA9","TA10","TA11","TA12")
meta = c("V","P","L","V","P","L")
names(meta) =   c("TA7","TA8","TA9","TA10","TA11","TA12")
```

Read in raw counts and metadata for run 2.
```{r}
for (sample in  c("TA7","TA8","TA9","TA10","TA11","TA12")){
  print(sample)
  mat_tmp = Read10X_h5(paste0("../20240710__115631__100724_Tomo_mouse_gutroll_run2/", datasets_r2[[sample]],"/nuclei_data.h5"))
  colnames(mat_tmp) = paste0(sample,"-",colnames(mat_tmp))
  meta_data = rbind(meta_data,data.frame(cell = colnames(mat_tmp), sample = sample, condition =  meta[sample]))
  mat = cbind(mat, mat_tmp)
}
```

Set rownames for the metadata.
```{r}
rownames(meta_data) = colnames(mat)
```

Create Seurat object
```{r}
xenium.obj = CreateSeuratObject(mat)
```

Add sample and condition
```{r}
xenium.obj$sample = meta_data$sample
xenium.obj$condition = meta_data$condition 
```

Make directory for output.
```{r}
directory = "../output/merged_analysis_nuclei/"
dir.create(directory)
```

Change matrix type to uint32_t.
```{r}
mat = convert_matrix_type(mat, type = "uint32_t")
```

Write matrix to a directory and load it.
```{r}
write_matrix_dir(mat = mat, dir = paste0(directory,'/bpcells_counts'), overwrite = TRUE)
counts.mat = open_matrix_dir(dir = paste0(directory,'/bpcells_counts'))
```

Create Seurat object.
```{r}
xenium.obj = CreateSeuratObject(counts.mat)

#remove unnecessary objects and free up memory.
rm(mat)
rm(mat_tmp)
gc()

#add metadata
xenium.obj$sample = meta_data$sample
xenium.obj$condition = meta_data$condition 

dim(xenium.obj)
```

We have 3410876 cells

Relaxed filtering - remove cells with zero counts. Here we don't really want holes in the tissue.
```{r}
xenium.obj = subset(xenium.obj, subset = nCount_RNA > 0)
dim(xenium.obj)
```

Now we have 3580743 cells.


# Analysis of all populations

Normalise data and find variable features.
```{r}
xenium.obj = NormalizeData(xenium.obj)
xenium.obj = FindVariableFeatures(xenium.obj)
```

Create sketch.
```{r}
xenium.obj = SketchData(
  object = xenium.obj,
  ncells = 500000,
  method = "LeverageScore",
  sketched.assay = "sketch"
)
xenium.obj
```

Save seurat object.
```{r}
saveRDS(xenium.obj, paste0(directory,"merged_BPCells.rds"))
```

Dimensionality reduction, clustering and UMAP calculation.
```{r}
DefaultAssay(xenium.obj) = "sketch"
xenium.obj = ScaleData(xenium.obj)
xenium.obj = RunPCA(xenium.obj, npcs = 30, features = rownames(xenium.obj))
xenium.obj = RunUMAP(xenium.obj, dims = 1:30, return.model = TRUE)
xenium.obj = FindNeighbors(xenium.obj, reduction = "pca", dims = 1:30)
xenium.obj = FindClusters(xenium.obj, resolution = 0.3)
```

Save Seurat object.
```{r}
saveRDS(xenium.obj, paste0(directory,"merged_BPCells_clustered.rds"))
```

Plot UMAP
```{r}
DimPlot(xenium.obj, cols = "polychrome", label = T)
ggsave(paste0(directory, "UMAP_res0.3.png"))

DimPlot(xenium.obj, group.by = "condition")
ggsave(paste0(directory, "UMAP_condition.png"))

DimPlot(xenium.obj, group.by = "sample", cols = "polychrome")
ggsave(paste0(directory, "UMAP_sample.png"))
```

Change multsession plan to 1 worker otherwise getMarkers function encounters problems.
```{r}
plan("multisession", workers = 1)
top5 = getMarkers(xenium.obj, "all_cells_res0.3", directory)
```

Project clusters from sketched analysis onto full dataset.
```{r}
xenium.obj = ProjectData(
  object = xenium.obj,
  assay = "RNA",
  full.reduction = "pca.full",
  sketched.assay = "sketch",
  sketched.reduction = "pca",
  umap.model = "umap",
  dims = 1:30,
  refdata = list(cluster_full = "seurat_clusters")
)

# Now that we have projected the full dataset, switch back to analyzing all cells
DefaultAssay(xenium.obj) = "RNA"

# Save seurat object.
saveRDS(xenium.obj, paste0(directory,"merged_BPCells_projected.rds"))
```

Change projected clusters to from character to factor.
```{r}
xenium.obj$cluster_full = factor(xenium.obj$cluster_full, levels = levels(xenium.obj@active.ident))
```

Plot UMAP.
```{r}
DimPlot(xenium.obj, group.by = "cluster_full", cols = "polychrome")
```

Create plot without cluster 20 (as it has less than 2 cells).
```{r}
p = DimPlot(xenium.obj[,xenium.obj@active.ident != "20"], group.by = "cluster_full", cols = "polychrome") + ylab("umap_2") + xlab("umap_1")

p + ggtitle("")

ggsave(paste0(directory, "all_populations_UMAP_3410861_cells.png"))
ggsave(paste0(directory, "all_populations_UMAP_3410861_cells.pdf"))
```

Switch back to sketched data.
```{r}
xenium.obj@active.assay = "sketch"
```

Plot UMAP of sketched data without cluster 20 (< 2 cells).
```{r}
p = DimPlot(xenium.obj[,xenium.obj@active.ident != "20"], cols = "polychrome") + ylab("umap_2") + xlab("umap_1")

p + ggtitle("")

ggsave(paste0(directory, "all_populations_UMAP_sketch_500000_cells.png"))

ggsave(paste0(directory, "all_populations_UMAP_sketch_500000_cells.pdf"))
```

Create dotplot of markers excluding cluster 20 (< 2 cells).
```{r}
markers = read.csv(paste0(directory,"all_cells_res0.3_markers.csv"))

markers = markers[markers$cluster != 20,]

xenium.obj@active.assay = "sketch"

xenium.obj$sketch_snn_res.0.3 = factor(xenium.obj$sketch_snn_res.0.3, levels = levels(xenium.obj@active.ident))
  markers %>%
    group_by(cluster) %>%
    dplyr::filter(avg_log2FC > 1) %>%
    slice_head(n = 5) %>%
    ungroup() -> top
p = DotPlot(xenium.obj[,xenium.obj$sketch_snn_res.0.3 != 20], unique(top$gene), group.by = "sketch_snn_res.0.3") 
p = p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(p)
ggsave(paste0(directory, "all_populations_res_0.3_marker_dotplot_v2.pdf"), height = 5, width = 13)
```

Create dotplot of markers excluding cluster 20 (< 2 cells) with Viridis colour scale. 
```{r}
xenium.obj$sketch_snn_res.0.3 = factor(xenium.obj$sketch_snn_res.0.3, levels = levels(xenium.obj@active.ident))
  markers %>%
    group_by(cluster) %>%
    dplyr::filter(avg_log2FC > 1) %>%
    slice_head(n = 5) %>%
    ungroup() -> top

p = DotPlot(xenium.obj[,xenium.obj$sketch_snn_res.0.3 != 20], features = unique(top$gene)) +
  guides(size = guide_legend(order = 1, reverse = TRUE), colour = guide_colourbar(order = 2)) + RotatedAxis() + scale_colour_viridis_c()
print(p)

ggsave(paste0(directory, "all_populations_res_0.3_marker_dotplot_tomo.pdf"), height = 6, width = 20)
```

Create dotplot of markers excluding cluster 20 (< 2 cells) with Viridis colour scale and no LFC cutoff. 
```{r}
xenium.obj$sketch_snn_res.0.3 = factor(xenium.obj$sketch_snn_res.0.3, levels = levels(xenium.obj@active.ident))
  markers %>%
    group_by(cluster) %>%
    slice_head(n = 5) %>%
    ungroup() -> top

p = DotPlot(xenium.obj[,xenium.obj$sketch_snn_res.0.3 != 20], features = unique(top$gene)) +
  guides(size = guide_legend(order = 1, reverse = TRUE), colour = guide_colourbar(order = 2)) + RotatedAxis() + scale_colour_viridis_c()
print(p)

ggsave(paste0(directory, "all_populations_res_0.3_marker_dotplot_noLFC_cutoff_tomo.pdf"), height = 6, width = 20)
```

Check cell numbers per cluster
```{r}
table(xenium.obj@active.ident)
```


# Epithelial cell analysis

Switch to RNA assay.
```{r}
xenium.obj@active.assay = "RNA"
```

Subset epithelial clusters, switch to sketched assay and perform dimensionality 
reduction and clustering.
```{r}
# subset cells in these clusters. Note that the data remains on-disk after subsetting
epi.obj = subset(xenium.obj, subset = cluster_full %in% c("0","11", "18","10", "12","4","17","1","19"))
dim(epi.obj)
DefaultAssay(epi.obj) = "sketch"

# recluster the cells
epi.obj = ScaleData(epi.obj)
epi.obj = RunPCA(epi.obj, npcs = 30, features = rownames(epi.obj))
epi.obj = RunUMAP(epi.obj , dims = 1:30,return.model = TRUE)
epi.obj = FindNeighbors(epi.obj , dims = 1:30)
epi.obj = FindClusters(epi.obj,resolution = 0.5)

saveRDS(epi.obj, paste0(directory,"epi_merged_BPCells.rds"))
```

Plot epithelial UMAP.
```{r}
DimPlot(epi.obj, cols = "polychrome", label = T)
ggsave(paste0(directory, "epiUMAP_res0.5.png"))

DimPlot(epi.obj, group.by = "condition")
ggsave(paste0(directory, "epiUMAP_condition.png"))

DimPlot(epi.obj, group.by = "sample", cols = "polychrome")
ggsave(paste0(directory, "epiUMAP_sample.png"))
```


Create dotplot of paneth and goblet cell markers.
```{r}
DotPlot(epi.obj, c("Lyz1","Defa17","Defa22","Defa24","Ang4","Muc2","Clca1","Tff3","Agr2"))
ggsave(paste0(directory, "epiDotplot_Paneth_Goblet.png"))
```

Create feature plots of known goblet cell markers.
```{r}
FeaturePlot(epi.obj, c("Muc2","Clca1","Tff3","Agr2"),max.cutoff = "q95")
ggsave(paste0(directory, "epiUMAP_Goblet.png"),height = 20, width = 20)
```

Create feature plots of known paneth cell markers.
```{r}
FeaturePlot(epi.obj, c("Lyz1","Defa17","Defa22","Defa24","Ang4"),max.cutoff = "q95")
ggsave(paste0(directory, "epiUMAP_Paneth.png"),height = 20, width = 20)
```

Project sketched clusters onto full dataset.
```{r}
epi.obj = ProjectData(
  object = epi.obj,
  assay = "RNA",
  full.reduction = "pca.full.epi",
  sketched.assay = "sketch",
  sketched.reduction = "pca",
  umap.model = "umap",
  dims = 1:30,
  refdata = list(cluster_full = "seurat_clusters")
)

# now that we have projected the full dataset, switch back to analyzing all cells.
DefaultAssay(epi.obj) = "RNA"

# save seurat object.
saveRDS(epi.obj, paste0(directory,"epi_merged_BPCells_projected.rds"))
```

Calculate numbers of cells per cluster per condition.
```{r}
res = table(epi.obj$condition,epi.obj$cluster_full)
write.csv(res, paste0(directory,"epi_merged_numbers_res0.5.csv"), row.names = F, quote = F)
```

Calculate fraction of cells per cluster per condition.
```{r}
write.csv(res/rowSums(res), paste0(directory,"epi_merged_fraction_res0.5.csv"), row.names = F, quote = F)
```

Plot epithelial UMAP - omit cluster 19 as < 3 cells.
```{r}
epi.obj$cluster_full = factor(epi.obj$cluster_full, levels = levels(epi.obj@active.ident))
p = DimPlot(epi.obj[,epi.obj$cluster_full != "19"], group.by = "cluster_full", cols = "polychrome") + ylab("umap_2") + xlab("umap_1")
p + ggtitle("")
ggsave(paste0(directory, "epi_UMAP_1979657_cells.png"))
ggsave(paste0(directory, "epi_UMAP_1979657_cells.pdf"))
```

Plot epithelial "sketch" UMAP - omit cluster 19 as < 3 cells.
```{r}
epi.obj@active.assay = "sketch"
p = DimPlot(epi.obj[,epi.obj@active.ident != "19"], cols = "polychrome") + ylab("umap_2") + xlab("umap_1")
p + ggtitle("")
ggsave(paste0(directory, "epi_UMAP_sketch_243214_cells.png"))
ggsave(paste0(directory, "epi_UMAP_sketch_243214_cells.pdf"))
```

Get markers for epithelial clusters.
```{r}
plan("multisession", workers = 1)
top5 = getMarkers(epi.obj, "epi_res0.5", directory)
```

Create dotplot of epithelial marker (DE) genes - omit cluster 19 as < 3 cells.
```{r}
markers = read.csv(paste0(directory,"epi_res0.5_markers.csv"))

markers = markers[markers$cluster != 19,]

epi.obj$sketch_snn_res.0.5 = factor(epi.obj$sketch_snn_res.0.5, levels = levels(epi.obj@active.ident))
  markers %>%
    group_by(cluster) %>%
    dplyr::filter(avg_log2FC > 1) %>%
    slice_head(n = 5) %>%
    ungroup() -> top
p = DotPlot(epi.obj[,epi.obj$sketch_snn_res.0.5 != "19"], unique(top$gene), group.by = "sketch_snn_res.0.5")
p = p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(p)
ggsave(paste0(directory, "epi_res_0.5_marker_dotplot_v2.pdf"), height = 5, width = 12)
```

Create dotplot of epithelial marker (DE) genes with viridis colour scheme.
```{r}
epi.obj$sketch_snn_res.0.5 = factor(epi.obj$sketch_snn_res.0.5, levels = levels(epi.obj@active.ident))
  markers %>%
    group_by(cluster) %>%
    dplyr::filter(avg_log2FC > 1) %>%
    slice_head(n = 5) %>%
    ungroup() -> top

p = DotPlot(epi.obj[,epi.obj@active.ident != "19"], features = unique(top$gene)) +
  guides(size = guide_legend(order = 1, reverse = TRUE), colour = guide_colourbar(order = 2)) + RotatedAxis() + scale_colour_viridis_c()
print(p)

ggsave(paste0(directory, "epi_res_0.5_marker_dotplot_tomo.pdf"), height = 6, width = 20)
```

Create dotplot of epithelial marker (DE) genes with viridis colour scheme and no LFC cutoff.
```{r}
epi.obj$sketch_snn_res.0.5 = factor(epi.obj$sketch_snn_res.0.5, levels = levels(epi.obj@active.ident))
  markers %>%
    group_by(cluster) %>%
    slice_head(n = 5) %>%
    ungroup() -> top

p = DotPlot(epi.obj[,epi.obj@active.ident != "19"], features = unique(top$gene)) +
  guides(size = guide_legend(order = 1, reverse = TRUE), colour = guide_colourbar(order = 2)) + RotatedAxis() + scale_colour_viridis_c()
print(p)

ggsave(paste0(directory, "epi_res_0.5_marker_dotplot_tomo_noLFC_cutoff.pdf"), height = 6, width = 20)
```

# Spatial analysis

Add cell centroids to xenium object.
```{r}
for (sample in  c("TA1","TA2","TA3","TA4","TA5","TA6")){
  cells = fread(paste0("../20240704__113302__040724_Tomo_mouse_gutroll_run1/", datasets_r1[[sample]],"/cells.csv.gz"))
  
  cell_centroid_df = data.frame(
          x = cells$x_centroid,
          y = cells$y_centroid,
          cell = paste0(sample, "-TA1-",cells$cell_id),
          stringsAsFactors = FALSE
        )
  cell_centroid_df = cell_centroid_df[cell_centroid_df$cell %in% colnames(xenium.obj),]
  centroid_data = list(
      "centroids" = CreateCentroids(cell_centroid_df)
  )

  
    coords <- CreateFOV(
      coords = centroid_data,
      type = c("centroids"),
      assay = "RNA"
  )
  
  xenium.obj[[sample]] = coords
}

for (sample in  c("TA7","TA8","TA9","TA10","TA11","TA12")){
  cells = fread(paste0("../20240710__115631__100724_Tomo_mouse_gutroll_run2/", datasets_r2[[sample]],"/cells.csv.gz"))
  
  cell_centroid_df = data.frame(
          x = cells$x_centroid,
          y = cells$y_centroid,
          cell = paste0(sample, "-TA1-",cells$cell_id),
          stringsAsFactors = FALSE
        )
  cell_centroid_df = cell_centroid_df[cell_centroid_df$cell %in% colnames(xenium.obj),]
  centroid_data = list(
      "centroids" = CreateCentroids(cell_centroid_df)
  )

  
    coords <- CreateFOV(
      coords = centroid_data,
      type = c("centroids"),
      assay = "RNA"
  )
  
  xenium.obj[[sample]] = coords
}
```

Create directory to save images.
```{r}
image_dir = paste0(directory,"image_dim_res0.3/")
dir.create(image_dir)
```

Make projected clusters active identity.
```{r}
xenium.obj@active.ident = factor(xenium.obj$cluster_full, levels = levels(xenium.obj@active.ident))
```

Create plots of gut rolls coloured by cluster.
```{r}
for (i in 1:12){
sample = paste0("TA",i)
ImageDimPlot(xenium.obj, size = 0.7, axes = T, fov = sample, cols = "polychrome")
ggsave(paste0(image_dir,"res0.3_image_dim_plot_", sample,".png"), height = 30, width = 20)
}
```

Create patchwork plot of all gut rolls coloured by cluster.
```{r}
plotList = list()
for (i in 1:12){
sample = paste0("TA",i)
print(sample)
p = ImageDimPlot(xenium.obj, size = 0.5, axes = T, fov = sample, cols = "polychrome")
p = p + theme(legend.position="none") + ggtitle(sample) + xlim(0,10000) + ylim(0,10000)
plotList[[sample]] = p
}

wrap_plots(plotList,
           ncol=3)
ggsave(paste0(directory,"res0.3_image_dim_plot.png"), height = 30, width = 30)
```

Add epithelial sub clusters to main xenium object.
```{r}
xenium.obj@active.assay = "RNA"
epi.obj@active.ident = factor(epi.obj$cluster_full, levels = levels(epi.obj@active.ident))
xenium.obj$epi_res0.5 = epi.obj@active.ident
```


Create directory to save epithelial cluster images.
```{r}
image_dir = paste0(directory,"image_dim_epi_res0.5/")
dir.create(image_dir)
```

Create plots of gut rolls coloured by epithelial cluster.
```{r}
for (i in 1:12){
sample = paste0("TA",i)
ImageDimPlot(xenium.obj, size = 0.7, axes = T, fov = sample, cols = "polychrome", group.by = "epi_res0.5")
ggsave(paste0(image_dir,"epi_res0.5_image_dim_plot_", sample,".png"), height = 30, width = 20)
}
```

Create patchwork plot of all gut rolls coloured by epithelial cluster.
```{r}
plotList = list()
for (i in 1:12){
sample = paste0("TA",i)
p = ImageDimPlot(xenium.obj, size = 0.4, axes = T, fov = sample, cols = "polychrome",group.by = "epi_res0.5")
p = p + theme(legend.position="none") + ggtitle(sample) + xlim(0,10000) + ylim(0,10000)
plotList[[sample]] = p
}

library(patchwork)
wrap_plots(plotList,
           ncol=3)
ggsave(paste0(directory,"epi_res0.5_image_dim_plot.png"), height = 30, width = 30)
```

Create plots of gut rolls coloured by Slc5a4a expression.
```{r}
image_dir = paste0(directory,"image_feature_Slc5a4a/")
dir.create(image_dir)

for (i in 1:12){
sample = paste0("TA",i)
ImageFeaturePlot(xenium.obj, "Slc5a4a", size = 0.7, axes = T, fov = sample)
ggsave(paste0(image_dir,"Slc5a4a_image_", sample,".png"), height = 30, width = 20)
}
```

Create plots of gut rolls coloured by Slc5a4a expression with q95 max cutoff.
```{r}
image_dir = paste0(directory,"image_feature_Slc5a4a_q95/")
dir.create(image_dir)

for (i in 1:12){
sample = paste0("TA",i)
ImageFeaturePlot(xenium.obj, "Slc5a4a", size = 1, axes = T, fov = sample, max.cutoff = "q95")
ggsave(paste0(image_dir,"Slc5a4a_image_", sample,".png"), height = 30, width = 20)
}
```

Create patchwork plot of all gut rolls coloured by epithelial cluster.
```{r}
plotList = list()
for (i in 1:12){
sample = paste0("TA",i)
p = ImageDimPlot(xenium.obj, size = 0.4, axes = T, fov = sample, cols = "polychrome",group.by = "epi_res0.5")
p = p + theme(legend.position="none") + ggtitle(sample) + xlim(0,10000) + ylim(0,10000)
plotList[[sample]] = p
}

wrap_plots(plotList,
           ncol=3)
ggsave(paste0(directory,"epi_res0.5_image_dim_plot.png"), height = 30, width = 30)
```

Create patchwork plots showing each epithelial cluster individually.
```{r}
res0.5_dir = paste0(directory,"res0.5_cluster_plots/")

dir.create(res0.5_dir)
for (cluster in unique(xenium.obj$epi_res0.5)){
  cluster = as.character(cluster)
  plotList = list()
  xenium.obj$COI = NA
  xenium.obj$COI[xenium.obj$epi_res0.5 == cluster] = cluster
  for (i in 1:12){
    sample = paste0("TA",i)
    p = ImageDimPlot(xenium.obj, size = 0.5, axes = T, group.by = "COI", fov = sample)
    p = p + theme(legend.position="none") + ggtitle(sample) + xlim(0,10000) + ylim(0,10000)
    plotList[[sample]] = p
  }
  wrap_plots(plotList,
           ncol=3)
  ggsave(paste0(res0.5_dir,"epi_res0.5_image_dim_plot_cluster",cluster,".png"), height = 30, width = 30)
}
```

# Save data

Save meta data.
```{r}
write.csv(xenium.obj@meta.data,paste0(directory,"nuclei_meta.csv"))
```

Save Xenium object.
```{r}
saveRDS(xenium.obj, paste0(directory,"merged_BPCells_coords.rds"))
```