---
title: "Run pseudobulk DE for each epithelial cluster"
output: html_notebook
---

Load libraries
```{r}
library(Seurat)
library(future)
plan("multisession", workers = 8)
library(ggplot2)
library(interp)
library(rdist)
library(Matrix)
library(dplyr)
library(future)
library(BPCells)
options(future.globals.maxSize = 3000*1024^2)
source("seurat_utility_functions.R")
library(data.table)
library(stringr)
library(DESeq2)
library(EnhancedVolcano)
```

Set directory.
```{r}
directory = "../output/merged_analysis_nuclei/"
```

# Create Pseudobulk

Read in epithelial object.
```{r}
epi.obj = readRDS(paste0(directory,"epi_merged_BPCells_projected.rds"))
```

Set active assay to RNA.
```{r}
epi.obj@active.assay = "RNA"
```

Create pseudobulk.
```{r}
pseudo_bulk.epi = AggregateExpression(epi.obj, assays = "RNA", group.by = c("condition", "sample", "cluster_full"))
```

Create metadata for pseudobulk.
```{r}
pseudo_bulk_meta = lapply(colnames(pseudo_bulk.epi$RNA),str_split_1, "_") 
pseudo_bulk_meta = do.call(rbind.data.frame,pseudo_bulk_meta)
colnames(pseudo_bulk_meta) = c("condition", "sample", "cluster")
rownames(pseudo_bulk_meta) = colnames(pseudo_bulk.epi$RNA)
```

Add slide information to pseudobulk.
```{r}
pseudo_bulk_meta$slide = ""
pseudo_bulk_meta$slide[pseudo_bulk_meta$sample %in% c("TA1","TA2","TA3")] = "S1"
pseudo_bulk_meta$slide[pseudo_bulk_meta$sample %in% c("TA4","TA5","TA6")] = "S2"
pseudo_bulk_meta$slide[pseudo_bulk_meta$sample %in% c("TA7","TA8","TA9")] = "S3"
pseudo_bulk_meta$slide[pseudo_bulk_meta$sample %in% c("TA10","TA11","TA12")] = "S4"
```

Remove cluster 19 (too few cells).
```{r}
pseudo_bulk.epi$RNA = pseudo_bulk.epi$RNA[,pseudo_bulk_meta$cluster != "19"]
pseudo_bulk_meta = pseudo_bulk_meta[pseudo_bulk_meta$cluster != "19",]
```

# Run DE 

Function to run DEseq2.
```{r}
run_deseq2 = function(condition1, condition2){
  results = list()
  for (cluster in unique(pseudo_bulk_meta$cluster)){
 
    selected = pseudo_bulk.epi$RNA[,(pseudo_bulk_meta$cluster == cluster) & (pseudo_bulk_meta$condition %in% c(condition1,condition2)) ]
    selected_meta = pseudo_bulk_meta[(pseudo_bulk_meta$cluster == cluster) & (pseudo_bulk_meta$condition %in% c(condition1,condition2)),]
    selected_meta$condition = factor(selected_meta$condition, levels = c(condition1,condition2))
    
    dds = DESeqDataSetFromMatrix(countData = selected,
                                  colData = selected_meta,
                                  design = ~slide + condition)
    
    dds = DESeq(dds)
    res = results(dds)
    
    res$cluster = cluster
    res$gene = rownames(res)
    
    res = res[order(res$pvalue),]
    res$gene = rownames(res)
  
    results[[cluster]] = res
  }
  results = do.call(rbind,results)
  
  # add adjusted p value that takes into account testing was done for multiple clusters.
  results$padj_overall = p.adjust(results$pvalue,method = "BH")
  return(results)
}
```

Run DEseq for each pairwise comparison.
```{r}
results_v_p = run_deseq2("V","P")
results_v_l = run_deseq2("V","L")
results_p_l = run_deseq2("P","L")
```

Write results to file.
```{r}
write.csv(results_p_l, paste0(directory, "lactation_vs_pregnant_res0.5_nuclei.csv"))
write.csv(results_v_p, paste0(directory, "pregnant_vs_virgin_res0.5_nuclei.csv"))
write.csv(results_v_l, paste0(directory, "lactating_vs_virgin_res0.5_nuclei.csv"))
```

Write significant (pval <0.05) results to file.
```{r}
results_p_l = results_p_l[!(is.na(results_p_l$padj_overall)),]
results_v_p = results_v_p[!(is.na(results_v_p$padj_overall)),]
results_v_l = results_v_l[!(is.na(results_v_l$padj_overall)),]

write.csv(results_p_l[results_p_l$padj_overall < 0.05,], paste0(directory, "lactation_vs_pregnant_res0.5_sig_nuclei.csv"))
write.csv(results_v_p[results_v_p$padj_overall < 0.05,], paste0(directory, "pregnant_vs_virgin_res0.5_sig_nuclei.csv"))
write.csv(results_v_l[results_v_l$padj_overall < 0.05,], paste0(directory, "lactating_vs_virgin_res0.5_sig_nuclei.csv"))
```


# Create volcano plots

Read in DE.
```{r}
results_p_l = read.csv(paste0(directory, "lactation_vs_pregnant_res0.5_nuclei.csv"))
results_v_l = read.csv(paste0(directory, "lactating_vs_virgin_res0.5_nuclei.csv"))
results_v_p = read.csv(paste0(directory, "pregnant_vs_virgin_res0.5_nuclei.csv"))
```

Create directory for volcano plots
```{r}
volcanoDir= "../output/merged_analysis_nuclei/volcanoPlots/"
dir.create(volcanoDir)
```

Function to make volcano plot.
```{r}
makeVolcano = function(results, cluster, name){
  res = results[results$cluster == cluster,]
  name = name
  plot_name = paste0(name," cluster ", cluster)
  EnhancedVolcano(res,
      title = plot_name,
      subtitle = "",
      lab = res$gene,
      x = 'log2FoldChange',
      y = 'padj',
      xlab = bquote(~Log[2]~ 'fold change'),
      ylab = bquote(~-Log[10]~adjusted~italic(P)),
      pCutoff = 0.05,
      FCcutoff = 1,
      pointSize = 4.0,
      labSize = 6.0,
      legendPosition = 'right',
      legendLabSize = 12,
      legendIconSize = 4.0,
      drawConnectors = TRUE,
      widthConnectors = 0.75)
  
  ggsave(paste0(volcanoDir,name, " cluster ", cluster,".pdf"), width = 8, height = 6)
}
```

Iterate through clusters and create volcano plots.
```{r}
for (cluster in 0:18){
  makeVolcano(results_p_l, cluster,  "Lactating vs pregnant")
  makeVolcano(results_v_p, cluster,  "Pregnant vs virgin")
  makeVolcano(results_v_l, cluster,  "Lactating vs virgin")
}
```

